Do expert pianists adapt their pedagogical demonstrations to novices' skills?

### 2023-01-17 paper/manuscript.Rmd
updated discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

To obtain experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists. The recordings were made based on the performance data from our previous study [@tominaga_2022]. All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (*Fig \ref{fig:stim}*). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

@@

>>>>

To obtain experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists. The recordings were made based on the performance data from our previous study [@tominaga_2022]. All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (*Fig \ref{fig:stim}*). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither articulation nor dynamics was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

@@

There are possibilities that it may be difficult in general for experts to flexibly adjust to different action parameters while teaching or they might have chosen to focus on the most salient parameters or the ones that they find most relevant. For example, when teaching dance, it is considered that good teachers need to identify and build the basic knowledge and skills first and then add complexity progressively from the basic foundation [@mainwaring_2010]. For example, when teaching social dance, a teacher started with a basic step as the hustle and then moved onto more complex steps progressively like the waltz and the cha cha [@lobel_2021]. Karl Leimer, a German music teacher and pianist, wrote in his booked that when doing finger exercises, students should perform with legato at first [@gieseking_1972]. Legato creates round and mellow tones, which is one of the most essential elements of piano touches in performance. In both dance and music examples, the ultimate goal of skill acquisition is that students are able to use multiple techniques flexibly while performing. However, it seems that students need to build complex skills based on basic ones during the learning process. Therefore, identifying and focusing on the most relevant problem for each student may be more effective to facilitate learning.

### 2023-01-17 paper/manuscript.tex
updated discussion
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

To obtain experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists. The recordings were made based on the performance data from our previous study (Tominaga et al., 2022). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (\emph{Fig \ref{fig:stim}}). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither dynamics nor articulation was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

@@

@@

>>>>

To obtain experimental control over learners' demonstrated proficiency in implementing particular techniques, we generated artificial recordings of novice piano performances instead of recruiting actual novice pianists. The recordings were made based on the performance data from our previous study (Tominaga et al., 2022). All the recordings were of the same piece but the recordings differed in the implementation of articulation and dynamics. According to the notated expressions in the sheet music, the proper performance of the piece required specific modulations with respect to both articulation and dynamics (\emph{Fig \ref{fig:stim}}). We generated four types of recordings. In one quarter of the recordings, both techniques were implemented; in one quarter, neither articulation nor dynamics was implemented; in the two remaining quarters, the piece was played with either only articulation or only dynamics implemented. This allowed us to investigate whether expert pianists in the role of teachers would make specific adjustments in response to the learners' demonstrated skills.

@@

There are possibilities that it may be difficult in general for experts to flexibly adjust to different action parameters while teaching or they might have chosen to focus on the most salient parameters or the ones that they find most relevant. For example, when teaching dance, it is considered that good teachers need to identify and build the basic knowledge and skills first and then add complexity progressively from the basic foundation (Mainwaring \& Krasnow, 2010). For example, when teaching social dance, a teacher started with a basic step as the hustle and then moved onto more complex steps progressively like the waltz and the cha cha (Lobel, 2021). Karl Leimer, a German music teacher and pianist, wrote in his booked that when doing finger exercises, students should perform with legato at first (Gieseking \& Leimer, 1972). Legato creates round and mellow tones, which is one of the most essential elements of piano touches in performance. In both dance and music examples, the ultimate goal of skill acquisition is that students are able to use multiple techniques flexibly while performing. However, it seems that students need to build complex skills based on basic ones during the learning process. Therefore, identifying and focusing on the most relevant problem for each student may be more effective to facilitate learning.

@@

\leavevmode\vadjust pre{\hypertarget{ref-gieseking_1972}{}}%
Gieseking, W., \& Leimer, K. (1972). \emph{Piano {Technique}}. {Dover Publications}.

\leavevmode\vadjust pre{\hypertarget{ref-lobel_2021}{}}%
Lobel, E. E. (2021). A {Model} for {Integrating Social} and {Creative Dance Forms} in a {Dance Education Course}. \emph{Journal of Dance Education}, \emph{21}(1), 44--47. \url{https://doi.org/10.1080/15290824.2020.1732984}

\leavevmode\vadjust pre{\hypertarget{ref-mainwaring_2010}{}}%
Mainwaring, L. M., \& Krasnow, D. H. (2010). Teaching the {Dance Class}: {Strategies} to {Enhance Skill Acquisition}, {Mastery} and {Positive Self-Image}. \emph{Journal of Dance Education}, \emph{10}(1), 14--21. \url{https://doi.org/10.1080/15290824.2010.10387153}
